### 2018-07-31 ms.tex
Fix up ms errors.

@@

A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\[0, 1\]$ while routine surveillance measures incidence $\[0, \infty\]$.
One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015}.

@@

We assign \rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
The former is based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy.}}
\begin{tabular}{l|l|l|l|l}
\hline
{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline \\
\multirow{6}{Incidence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
                                          & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
\multirow{6}{Prevalence} & \multirow{3}{Pearson} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
                                         & \multirow{3}{Spearman} & Indonesia & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Madagascar & 0.1 &. 0.2 & {\bf 0.3}\\
                   & Senagal & 0.1 &. 0.2 & {\bf 0.3}\\
\end{tabular}
\begin{flushleft}
Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

>>>>

% multirow for multiple row tables. 
\usepackage{multirow}

@@

A model that could combine point surveys and aggregated surveillance has great potential if it could leverage the strengths of both aggregated surveillance data and point survey data.
One major barrier to this modelling approved us that these two data sources are on different scales: point surveys are a measurement of prevalence $\lbrack 0, 1\rbrack$ while routine surveillance measures incidence $\lbrack 0, \infty\rbrack$.
One approach to combining these datasets is to use a seperately estimated model that maps one scale to another such as \cite{cameron2015}.

@@

We assign $\rho$ and $\sigma_u$ penalised complexity priors as well such that $P(\sigma_v > 0.05) = 0.00001$ and $P(\sigma_w > 0.05) = 0.00001$. 
The former is based on a comparison of the variance of Poisson random variables, with rates given by the number of cases observed, and an independently derived upper and lower bound for three case counts \ref{cibulskis}.
We found that an iid effect with a standard deviation of 0.05 would be able to account for the discrepancy.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
          & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{3mm} \\ 
Prevalence & Pearson & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\vspace{1mm}\\ 
            & Spearman & Indonesia & 0.1 & 0.2 & {\bf 0.3}\\
                   && Madagascar & 0.1 & 0.2 & {\bf 0.3}\\
                   && Senagal & 0.1 & 0.2 & {\bf 0.3}\\
\end{tabular}
\begin{flushleft}
Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}
